\textbf{Assignment Submission} All students should submit their assignments electronically via GradeScope. No handwritten work will be accepted. Math formulas \textbf{must} be typeset using \LaTeX\ or other word processing software that supports mathematical symbols (E.g. Google Docs, Microsoft Word). Simply sign up on Gradescope and use the course code V84RPB. Please use your UW NetID if possible.
\\
\\
For the non-coding component of the homework, you should upload a PDF rather than submitting as images. We will use Gradescope for the submission of code as well. Please make sure to tag each part correctly on Gradescope so it is easier for us to grade. There will be a small point deduction for each mistagged page and for each question that includes code. Put all the code for a single question into a single file and upload it. Only files in text format (e.g. .txt, .py, .java) will be accepted. \textbf{There will be no credit for coding questions without submitted code on Gradescope, or for submitting it after the deadline}, so please remember to submit your code.
\\
\\
\textbf{Coding} You may use any programming languages and standard libraries, such as NumPy and PySpark, but you may not use specialized packages and, in particular, machine learning libraries (e.g. sklearn, TensorFlow), unless stated otherwise. Ask on the discussion board whether specific libraries are allowed if you are unsure. 

\textbf{Late Day Policy } All students will be given two no-questions-asked late periods, but only one late period can be used per homework and cannot be used for project deliverables. A late-period lasts 48 hours from the original deadline (so if an assignment is due on Thursday at 11:59 pm, the late period goes to the Saturday at 11:59pm Pacific Time).
\\
\\
\textbf{Academic Integrity} We take \href{https://www.cs.washington.edu/academics/misconduct}{academic integrity} extremely seriously. 
We strongly encourage students to form study groups. Students may discuss and work on homework problems in groups. However, each student must write down the solutions and the code independently. In addition, each student should write down the set of people whom they interacted with. 
\\
\vfill
Discussion Group (People with whom you discussed ideas used in your answers):
\\
\vfill
On-line or hardcopy documents used as part of your answers: 
\\
\vfill
I acknowledge and accept the Academic Integrity clause.\\*[3ex]
\bigskip
\textit{(Signed)}\hrulefill

\vfill